Experiment 2 of 4

### 2016-10-02 experiments/e2/writeup/e2-analysis.Rmd
renaming e2 to e2-analysis

```{r preprocessing}
source('e2-preprocessing.R')
if( !file.exists('e2-b-data.txt') ) {
  dat <- gatherData() 
  dat <- declareImpossibleRT(dat)
  #dat <- removeImpossibleTrials(dat)
  dat <- subset(dat, select=c(Subject, Trial, Item, c_Itm, 
                              discriminability, 
                              Instruction,
                              nchar_instr,
                              Vagueness, Number, Order, Quantity, 
                              c_Vag, c_Num, c_Ord, c_Qty,
                              NaType, response_category, 
                              isBorderline, RT, RT_log)
  )
  write.table(dat, file='e2-b-data.txt', sep='\t', quote=FALSE, row.names = FALSE)
}
```

>>>>

```{r preprocessing}
source('e2-preprocessing.R')
if( !file.exists('e2-data.txt') ) {
  dat <- gatherData() 
  dat <- declareImpossibleRT(dat)
  #dat <- removeImpossibleTrials(dat)
  dat <- subset(dat, select=c(Subject, Trial, Item, c_Itm, 
                              discriminability, 
                              Instruction,
                              nchar_instr,
                              Vagueness, Number, Order, Quantity, 
                              c_Vag, c_Num, c_Ord, c_Qty,
                              NaType, response_category, 
                              isBorderline, RT, RT_log)
  )
  write.table(dat, file='e2-data.txt', sep='\t', quote=FALSE, row.names = FALSE)
}
```
